EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-21 draft.tex
Answers
Response to a12e4f1
Carification
References comment in 58d851e
Clarification
refernces 071d207

When comparing the results in this section, we performed the Wilcoxon Signed-Rank test, with a
significance level of 5\%. We indicate with an asterisk those results that are
not significant. % Where? - JJ

To measure the speedup obtained by the addition of workers, we will use the
number of evaluations per second, instead of the time required to finish an
instance of a problem. The reason for this is that in some cases reaching the
desired target can require less work, because we are using a stochastic search. 
We are going to measure the total increase of work done in a second by adding more workers.

\begin{table}[h!tbp]
  \caption{Speedup by worker and dimension, taking one worker as the
    baseline.}
% Clarify here what you are measuring. Number of evaluations for
% whatever divided by whatever - JJ
  \label{tab:speedup-table}
  \vspace{0.25cm}
  \centering

@@

In this paper we have presented the EvoSwarm framework for 
the reproducible execution of experiments with an event-based, cloud-native architecture 
suitable for hosting multi-population, multi-algorithm optimization
methods. 
The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy for scientists and practitioners to develop and deploy
% The last version still uses Docker Compose? - JJ
multi-algorithm distributed experiments. The model implemented by the
framework is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data; populations are the messages that flow in this stream. We show the differences of the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature, and highlight the 
advantages for conducting asynchronous multi-population algorithms.

@@

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms such as the ones implemented in this kind of framework.
We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework 
for visualization and definition of the optimization problems.
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The
hybrid method using both algorithms 
achieved better results and, in most cases, needed fewer evaluations. % Clarify if they actually achieve that way superlinear improvements - JJ

>>>>

When comparing the results in this section, we performed the Wilcoxon Signed-Rank test, with a
significance level of 5\%. We indicate with an asterisk those results that are
not significant throughout the tables of this section.  % Where? - JJ
% Answered - Mario
To measure the speedup obtained by the addition of workers, we will use the
number of evaluations per second, instead of the time required to finish an
instance of a problem. The reason for this is that in some cases reaching the
desired target can require less work, because we are using a stochastic search. 
We are going to measure the total increase of work done in a second by adding more workers.

\begin{table}[h!tbp]
  \caption{Speedup by worker and dimension, taking one worker as the
    baseline. Speedup is obtained by dividing the evaluation ratio of the baseline by the 
    ratio of the increased number of workers.}
% Clarify here what you are measuring. Number of evaluations for
% whatever divided by whatever - JJ
% Done - Mario
  \label{tab:speedup-table}
  \vspace{0.25cm}
  \centering

@@

In this paper we have presented the EvoSwarm framework for 
the reproducible execution of experiments with an event-based, cloud-native architecture 
suitable for hosting multi-population, multi-algorithm optimization
methods. 
The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy for scientists and practitioners to develop and deploy
% The last version still uses Docker Compose? - JJ
% Well it uses docker-compose files, and these files are  
% converted to tasks and services by the ECS-CLI. -Mario
% It still can be used to run the application locally - Mario 
multi-algorithm distributed experiments. The model implemented by the
framework is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data; populations are the messages that flow in this stream. We show the differences of the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature, and highlight the 
advantages for conducting asynchronous multi-population algorithms.

@@

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms such as the ones implemented in this kind of framework.
We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework 
for visualization and definition of the optimization problems.
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The
hybrid method using both algorithms 
achieved better results and, in most cases, needed fewer evaluations.

% Clarify if they actually achieve that way superlinear improvements - JJ
% They should, in this experiment we only tested the #FEs, but they imply 
% a superlinear improvements as we established in the previous section - Mario
